Workflow

### 2014-07-29 Workflow/Workflow.Rmd
Workflow now accounts for DownloadResults.R

---
title: "Workflow"
author: "Matthew Kuperus Heun"
date: "July 25, 2014"
output: html_document
---

@@

### Add new data
* Add a file named `<Source>.txt` in the data directory.   
* Edit the `Packages/EconData/R/Constants.R` file to include `<Source>` in the `dataSource` variable.   
* Add any Excel workbooks or other metadata in `data/Excel Workbooks/<Source>`.

### Create historical data frame
* Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.
The file will be stored at `Packages/EconData/data/<Source>.rda`.
This command is fast; it can be run on a laptop.    
* Build and reload the `EconData` package.    
* Push the changes to GitHub.   
* On acc, Pull from GitHub.     
* On dahl (node-00), say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.   
This command doesn't work on fs1 or any of the nodes (node-01 through node-42).

@@

### Add processed results to the EconData package
* From acc, push the changes to GitHub to make the new files available.
* Pull from GitHub on a local laptop, and build and reload the `EconData` package.

At this point, all new results should be available in the `EconData` package.
Objects will be named:

* `<Source>_Coeffs` (from the file `Packages/EconData/data/<Source>_Coeffs.rda`)  
* `<Source>_Fitted` (from the file `Packages/EconData/data/<Source>_Fitted.rda`)  
* `<Source>_OrigModels` (from the file `Packages/EconData/data/<Source>_OrigModels.rda`)

>>>>

---
title: "Workflow"
author: "Matthew Kuperus Heun"
date: "29 July 2014"
output: html_document
---

@@

### Add new data
* Add a file that contains the historical data from `<Source>` (name should be `<Source>.txt`) 
in the `data` directory at the top level of the repository.   
* Add any Excel workbooks or other metadata in `data/Excel Workbooks/<Source>`.

### Create historical data frame
* Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.
The file will be stored at `Packages/EconData/data/<Source>.rda`.
This command is fast; it can be run on a laptop.    
* Build and reload the `EconData` package.    
* Push the changes to GitHub.   
* On acc, Pull from GitHub.     
* On node-00, say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.
This makes the historical data available to the nodes of dahl.
This command doesn't work from fs1 or any of the other nodes of dahl (node-01 through node-42).

@@

### Download post-processed results to local machine
* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source> -d`, where `<user>` is 
a username on dahl, `<Source>` is the data source of interest, and `-d` will 
print the files to be transferred to the local machine, rather than transfer them.
* Verify that the list of files to be transferred looks right.
* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source>` to download the files.

### Add processed results to the EconData package
* On the local machine, build and reload the `EconData` package.

At this point, all new results should be available in the `EconData` package on the local machine.
Objects will be named:

* `<Source>_Coeffs` (from the file `Packages/EconData/data/<Source>_Coeffs.rda`)  
* `<Source>_Fitted` (from the file `Packages/EconData/data/<Source>_Fitted.rda`)  
* `<Source>_Models` (from the file `Packages/EconData/data/<Source>_OrigModels.rda`)
